Untitled Draft

### 2023-03-17 doc/manuscript.Rmd
increase table spacing

\renewcommand{\arraystretch}{0.65}

@@

```{r load-targets, include=FALSE}
tar_load(model_list_by_age)
tar_load(data_clean)
tar_load(purdy_pictures)
tar_load(model_tables)
tar_load(demog_table)
tar_load(table_1)
pretty <- function(x) format(x, big.mark = ",")
```

@@

The aggregated data-set describes `r nrow(data_clean) |> pretty()` observations of daily physical activity and sleep from `r length(unique(data_clean$participant_id)) |> pretty()` unique participants.
Table \@ref(tab:demo-participants) shows demographic information for all participants.
A table of study characteristics can be found in supplementary materials.

```{r demo-participants}
papaja::apa_table(demog_table,
  caption = "Participant characteristics",
  note = glue::glue("For categorical variables the value is the count, and percentage. For numeric variables the value is the Mean and SD. N = {format(length(unique(table_1$participants$participant_id)),big.mark = ',')}"),
  landscape = TRUE,
  col_spanners = list("Age group" = c(2, 6))
)
```

>>>>

\renewcommand{\arraystretch}{0.7}

@@

```{r load-targets, include=FALSE}
tar_load(model_list_by_age)
tar_load(data_clean)
tar_load(purdy_pictures_by_age)
tar_load(model_tables)
tar_load(demog_table)
pretty <- function(x) format(x, big.mark = ",")
```

@@

```{r}
n_participants <- length(unique(data_clean$participant_id))
```

The aggregated data-set describes `r nrow(data_clean) |> pretty()` observations of daily physical activity and sleep from `r n_participants |> pretty()` unique participants.
Table \@ref(tab:demo-participants) shows demographic information for all participants.
A table of study characteristics can be found in supplementary materials.

```{r demo-participants}
papaja::apa_table(demog_table,
  caption = "Participant characteristics",
  note = glue::glue("For categorical variables the value is the count, and percentage. For numeric variables the value is the Mean and SD. N = {n_participants |> pretty()}"),
  landscape = TRUE,
  col_spanners = list("Age group" = c(2, 6))
)
```
